Investigating magnetic dynamo evolution with \TESS\ field dwarfs

### 2017-10-06 ms.tex
adding real number of stars

\citet{oh2016} identified over 10,000 comoving pairs of stars using proper
motions from the first \Gaia\ data release.
Of these, 18 dwarfs and subgiants in 9 pairs have \RAVE\ radial velocities
consistent with being comoving and are already in the Candidate Target List.
Following \citet{campante2016} we calculate that these stars have oscillation
detection probabilities greater than 50\%, based on their \RAVE-on
T$_{\mathrm{eff}}$, $\log g$ and radii \citep{casey2017}.
Since these stars would make interesting targets for both asteroseismology and
exoplanet search, we include a list with this proposal.
The stars in these pairs are likely recently disrupted binaries so we
expect them to have similar ages and measuring their rotation periods will
therefore provide a test of gyrochronology.
An additional 5000 bright comoving pair candidates lie in the southern
ecliptic hemisphere and will be ideal FFI targets for gyrochronology studies.
{\bf We will use the rotation periods of comoving stars to quantify the
accuracy and precision of gyrochronology.}

>>>>

\citet{oh2016} identified over 10,000 comoving pairs of stars using proper
motions from the first \Gaia\ data release.
Of these, 8 dwarfs and subgiants in 4 pairs have \RAVE\ radial velocities
consistent with being comoving and are already in the Candidate Target List.
Following \citet{campante2016} we calculate that these stars have oscillation
detection probabilities greater than 0.85, based on their \RAVE-on
T$_{\mathrm{eff}}$, $\log g$ and radii \citep{casey2017} and their observation
baseline, from {\tt tvguide}.
Since these stars would make interesting targets for both asteroseismology and
exoplanet search, we include a list with this proposal.
The stars in these pairs are likely recently disrupted binaries so we
expect them to have similar ages and measuring their rotation periods will
therefore provide a test of gyrochronology.
An additional 5000 bright comoving pair candidates lie in the southern
ecliptic hemisphere and will be ideal FFI targets for gyrochronology studies.
{\bf We will use the rotation periods of comoving stars to quantify the
accuracy and precision of gyrochronology.}
